Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-23 paper.tex
Updated Experiments
Rosenbrock tables included.

@@

>>>>

    \begin{table}[]
        \scriptsize
        \centering
        \caption{Rosenbrock Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_rosenbrock5}
        \begin{tabular}{@{}lllll@{}}
        \toprule
        \multicolumn{5}{l}{\textbf{Function Rosenbrock - 5 Dimensions}} \\ \midrule
        & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
        \textbf{Xover Mutation} & 4.65E-03 & 8.29E-03 & 500,000 & 646.4 \\
        \textbf{Elite Projection} & 9.62E-07 & 1.86E-06 & 307,878 & 427.0 \\
        \textbf{All Random} & 8.30E-06 & 1.58E-05 & 491,400 & 697.8 \\ \bottomrule
        \end{tabular}
        \end{table}

@@

    \begin{table}[]
        \scriptsize
        \centering
        \caption{Rosenbrock Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_rosenbrock10}        
        \begin{tabular}{@{}lllll@{}}
        \toprule
        \multicolumn{5}{l}{\textbf{Function Rosenbrock - 10 Dimensions}} \\ \midrule
        & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
        \textbf{Xover Mutation} & 1.35E+00 & 9.83E-01 & 1,000,000 & 1,384.3 \\
        \textbf{Elite Projection} & 4.26E-02 & 4.34E-02 & 1,000,000 & 1,146.0 \\
        \textbf{All Random} & 4.27E-02 & 6.02E-02 & 952,038 & 1,147.8 \\ \bottomrule
        \end{tabular}
        \end{table}
